Structured Versus Decorated Cospans

### 2021-01-11 cospans.tex
Theorem 3.1: "finite colimits" |-> "finite coproducts"

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.  In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

>>>>

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.  In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve these \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}
